This appendix contains the full robustness battery. The
main text retains only the consolidated
Table~\ref{tab:rp_robustness} (printed once, in
\S\ref{ssec:main_baseline}); the design choices and
interpretation discussed in
\S\ref{sec:robustness} are reported here in full detail.

\subsection{Alternative AI-answerability
measures}\label{app:rob_ai_measures}

The four pre-treatment AI-answerability measures and the
DDD coefficient each delivers are:

\begin{center}
\small
\begin{tabular}{lrrrr}
\toprule
Measure & $\hat\beta$ & SE & $p$ & $N$ \\
\midrule
Structural index (baseline) & $-0.108$ & 0.046 & 0.021 &
164{,}351 \\
$z$-score composite          & $-0.138$ & 0.052 & 0.008 &
164{,}351 \\
PCA composite                & $-0.045$ & 0.020 & 0.024 &
164{,}351 \\
Quartile rank                & $-0.210$ & 0.074 & 0.005 &
164{,}351 \\
\bottomrule
\end{tabular}
\end{center}

The structural variant is the most conservative; the
quartile rank is the largest in absolute magnitude
(coarsening adds variance to the contrast).

\subsection{Sample restrictions}\label{app:rob_samples}

Top-50 tags by pre-period volume: $-0.207$ ($p=0.026$).
Top-75 tags: similarly negative coefficient. Interquartile
band on pre-treatment slope (75 tags closest to median
slope): $-0.155$ ($p=0.009$). Each of the four quartiles of
pre-treatment slope returns a negative coefficient:
quartile 1 (steepest decline) $-0.06$;
quartile 2 $-0.19$;
quartile 3 $-0.08$;
quartile 4 (steepest growth) $-0.32$. The result is not
driven by tags with extreme pre-trends.

Leave-one-out / jackknife: dropping the top-1 (python),
top-5, top-10, and top-20 tags returns coefficients
between $-0.166$ and $-0.196$. Jackknifing each of the
top-10 tags individually returns a range
$[-0.166, -0.136]$. The aggregate result is not an
artefact of a small number of large communities.

\subsection{Alternative outcomes}\label{app:rob_outcomes}

Replacing the outcome by $\log(1+\text{unique users})$
returns $\hat\beta=-0.133$ ($p=0.010$), confirming that the
substitutability gradient also operates on the count of
distinct authors. Counts-based estimation via PPML
\citep{santossilva2006log} returns $\hat\beta=-0.098$
($p=0.027$). Fractional tag counts---weighting each
question by $1/n_{\text{top-100 tags}}$---return
$\hat\beta=-0.134$ ($p=0.005$).

\subsection{Inference}\label{app:rob_inference}

CR1 clustering by tag: SE $=0.052$. Two-way clustering
on tag and week \citep{cameron2011robust}: SE $=0.052$
(within-tag serial correlation dominates the variance
budget). Wild cluster bootstrap with 9{,}999 Rademacher
replicates and the null imposed \citep{cameron2008wild}:
$p < 0.005$.

\subsection{Continuous-substitutability
specification}\label{app:rob_continuous}

Replacing the binary substitutable indicator with a
continuous embedding-derived substitutability score
returns
$\hat\beta = -0.039$ ($p=0.004$) under the structural
answerability measure and $-0.053$ ($p=0.0009$) under the
$z$-score composite. The continuous estimate is
approximately one-third the size of the binary estimate
(expected: the continuous score shrinks the substitutable
vs.\ non-substitutable contrast).

\subsection{Pre-trend sensitivity
bounds}\label{app:rob_honest}

The sensitivity exercise of \S\ref{ssec:id_honest_did}
yields the following robust 95\% confidence sets under
increasing $\bar M$ (the relative-magnitude bound on the
post-period deviation from parallel trends, in units of
the largest pre-period deviation):

\begin{center}
\small
\begin{tabular}{rrl}
\toprule
$\bar M$ & Robust 95\% CI & Contains 0? \\
\midrule
0.00 & $[-0.098, -0.029]$ & No \\
0.25 & $[-0.117, -0.021]$ & No \\
0.50 & $[-0.136, -0.010]$ & No \\
0.75 & $[-0.159, +0.010]$ & Yes (breakdown) \\
1.00 & $[-0.186, +0.029]$ & Yes \\
1.50 & $[-0.232, +0.075]$ & Yes \\
2.00 & $[-0.281, +0.124]$ & Yes \\
\bottomrule
\end{tabular}
\end{center}

Breakdown occurs at $\bar M = 0.75$ under the official
HonestDiD $\Delta^{\text{RM}}$ implementation with the
full cluster-robust event-study VCV
(\S\ref{ssec:id_honest_did}). Earlier versions of this
paper reported a bespoke calculation with a different
threshold; the full-$\Sigma$ \texttt{honestdid}-based
bound is the reference value we use going forward.

\subsection{Summary of what the robustness rules
out}\label{app:rob_summary}

In combination, the robustness battery rules out:
\begin{itemize}
\item that the result is an artefact of one particular AI
measure (all four are negative);
\item that the result is driven by extreme tags
(leave-one-out, IQR band, slope-quartile stratification);
\item that the result is a counting artefact of multi-tag
questions (fractional counts);
\item that the result is a clustering or distributional
artefact (two-way clustering, wild bootstrap, PPML);
\item that the result is an extrapolation of pre-trends
(HonestDiD $\Delta^{\text{RM}}$ full-VCV breakdown
$\bar M = 0.75$, placebo cutoffs with opposite sign,
rolling placebos);
\item that the result is driven by the GitHub Copilot
release (Copilot has the opposite sign);
\item that the result is sensitive to specific specification
choices (100\% negative across 32 cells).
\end{itemize}
What the robustness does \emph{not} rule out is the
concern that the binary substitutability classification is
heuristic. We address this directly in
\S\ref{sec:validation} with three independent classifiers
and Fleiss' $\kappa$.
