\label{sec:validation_body}

The substitutable / non-substitutable binary classification is
the central measurement decision. The baseline classifier is
heuristic (title-keyword patterns plus body-length and
code-block features, mapped to seven categories then collapsed to
a binary label). We validate it against two independent
sentence-embedding classifiers on a stratified random sample of
10{,}000 questions: \texttt{all-MiniLM-L6-v2} and
\texttt{all-mpnet-base-v2} (different architectures and training
corpora, so their mutual agreement is a stronger signal than
either with the heuristic), each assigning questions to the
nearest category centroid in cosine space.

\subsection{Agreement and the high-agreement
subsample}\label{ssec:val_kappa}\label{ssec:val_high_agree}\label{ssec:val_protocol}\label{ssec:val_crosstab}\label{ssec:val_implications}

The two embedding classifiers agree with each other in the
substantial range (binary Cohen's $\kappa=0.67$; 7-way $0.68$),
above either's agreement with the heuristic ($\kappa=0.44$--$0.46$
binary), and the multi-rater Fleiss' $\kappa$ is $0.52$ for the
binary label and $0.40$ for the seven-way category---moderate
rather than strong. For $70.5\%$ of the sample all three
classifiers agree on the binary label, and within this
high-agreement subsample the DDD point estimate is statistically
indistinguishable from the full-sample baseline ($\approx-0.11$),
so the result is not driven by the heuristic's disagreement
cases. The heuristic is more conservative than the embedding
majority (labelling $28.6\%$ versus $22.4\%$ non-substitutable),
which under-counts non-substitutable cells and if anything
attenuates $\beta_{\text{DDD}}$. The substitutability concept
thus has reasonably stable semantic content across embeddings,
while the noisier seven-way split ($\kappa=0.40$) means the
question-type decomposition (\S\ref{ssec:mech_by_type}) should be
read as illustrative of the gradient---consistent with the
negative advanced-architecture coefficient---rather than as
precise category-by-category estimates. We retain the
embedding-validated heuristic as the funnel-building baseline and
use the continuous embedding score as a co-primary check; a
contemporary-LLM scorer would embed a specific model generation
into the measure and introduce circularity, which the zero-budget
design avoids. Full $\kappa$ tables and the cross-tabulation are
in the replication package.
